Open archaeology, open source?

### 2024-02-02 analysis/_03-data_methodology.qmd
Update open-archaeo and GitHub data

```{r data-oarch}
# TODO: update and replace with local file before submission
read_csv("https://github.com/zackbatist/open-archaeo/raw/master/open-archaeo.csv") |>
  mutate(category = na_if(category, "?")) ->
  oarch

# Extract clean repos from GitHub URLs
oarch |>
  mutate(
    gh_repo = str_match(oarch$github, "^https://github.com/([\\w-\\.]+/[\\w-\\.]+)/?.*?$")[,2]
  ) ->
  oarch
```

@@

# Exclude from GitHub API data collection because does not have own repo
oarch$gh_repo[oarch$item_name == "ArchaeoLines"] <- NA
```

@@

```{r data-github}
# If cached data at `analysis/data/derived_data/oarch.RData` is present, this
# chunk will prefer to load it rather than make requests to the GitHub API.
# Delete this file to fetch fresh data from the GitHub or modify 
# `cached_gh_data` to read a different cached version.
#
# Note that fetching data from the GitHub API takes some time and is subject to
# a rate limit:
# <https://docs.github.com/en/rest/overview/resources-in-the-rest-api#rate-limiting>
#
# You will need to authenticate authenticate with GitHub credentials to get a
# rate limit sufficient to obtain the required data, see 
# <https://gh.r-lib.org/articles/managing-personal-access-tokens.html>
# for options on how to do this.
cached_gh_data <- here("analysis/data/derived_data/oarch.RData")
if (!file_exists(cached_gh_data)) {
  oarch$gh_repo_info <- map(oarch$gh_repo, gh_repo_info, .progress = TRUE)
  oarch$gh_langs <- map(oarch$gh_repo, gh_lang, .progress = TRUE)
  oarch$gh_contribs <- map(oarch$gh_repo, gh_contrib, .progress = TRUE)
  oarch$gh_issues <- map(oarch$gh_repo, gh_issue, .progress = TRUE)
  oarch$gh_comments <- map(oarch$gh_repo, gh_comment, .progress = TRUE)
  oarch$gh_commits <- map(oarch$gh_repo, gh_commit, .progress = TRUE)
  saveRDS(oarch, cached_gh_data)
}
oarch <- readRDS(cached_gh_data)
```

@@

Where applicable, we obtained more detailed information about each repository's contents and contribution histories from the GitHub API using the R package `gh` [@csardi2023].
This included metadata on the GitHub repository and the programming languages it uses, as well as detailed data on each repository's individual contributors, commits, issues and comments.
We opted to only collect repository data from GitHub because it is the most popular forge platform used by open-archaeo projects (@tbl-forges).
This means that projects that do not use version control (`r percent(p_no_vc)` of the total), or host it elsewhere (`r percent(p_no_github)` of the total), are excluded from these parts of the analysis, though we were still able to perform an analysis of their contents and authorship from the data included in open-archaeo itself.

The open-archaeo dataset and the supplemental data from the GitHub API provide us with a rich resource to explore the makeup of the archaeological software development scene.
We apply exploratory data analysis methods to break down and visualize the data, so that we may ascertain overall trends [@tukey1977].
In @sec-open-archaeology, our focus is on examining the general state of open source archaeological software and resource development.
In @sec-collaboration, we refine our analysis to examine development processes, with specific focus on collaborative experiences.
Finally, in @sec-network, we apply network analysis methods to investigate the formation of broader collaborative communities.
Our analyses combine to support our objectives of understanding what kinds of software and resources archaeologists are making, and how they create these tools in response to specific needs and use-cases, as afforded by offline social and professional connections, and within the context of an emerging community of practice.

The quantitative analyses and figures presented here were generated with `r version$version.string` [@rcoreteam2023].
The full data and code is available in the compendium that accompanies this paper [@roe2023] <!-- reference should be updated to reflect the actual version number and date -->.

>>>>

```{r data-oarch}
# open-archaeo version 2024-02-02
# https://doi.org/10.5281/zenodo.10611198
oarch <- read_csv(here("analysis/data/raw_data/open-archaeo_2024-02-02.csv"))

# Extract clean repos from GitHub URLs
oarch <- mutate(
  oarch,
  gh_repo = str_match(oarch$github, "^https://github.com/([\\w-\\.]+/[\\w-\\.]+)/?.*?$")[,2]
)
```

@@

# Exclude from GitHub API data collection because they part of a larger
# repository (or forked from one)
oarch$gh_repo[oarch$item_name == "ArchaeoLines"] <- NA
oarch$gh_repo[oarch$gh_repo == "carpentries-incubator/R-archaeology-lesson"] <- NA
```

@@

```{r data-github}
# If cached data at `analysis/data/derived_data/oarch.RData` is present, this
# chunk will prefer to load it rather than make requests to the GitHub API.
# Delete this file to fetch fresh data from the GitHub or modify 
# `cached_gh_data` to read a different cached version.
#
# Note that fetching data from the GitHub API takes some time and is subject to
# a rate limit:
# <https://docs.github.com/en/rest/overview/resources-in-the-rest-api#rate-limiting>
#
# You will need to authenticate authenticate with GitHub credentials to get a
# rate limit sufficient to obtain the required data, see 
# <https://gh.r-lib.org/articles/managing-personal-access-tokens.html>
# for options on how to do this.
cached_gh_data <- here("analysis/data/derived_data/oarch.RData")
if (!file_exists(cached_gh_data)) {
  oarch$gh_repo_info <- map(oarch$gh_repo, gh_repo_info, .progress = TRUE)
  oarch$gh_langs <- map(oarch$gh_repo, gh_lang, .progress = TRUE)
  oarch$gh_contribs <- map(oarch$gh_repo, gh_contrib, .progress = TRUE)
  oarch$gh_issues <- map(oarch$gh_repo, gh_issue, .progress = TRUE)
  oarch$gh_comments <- map(oarch$gh_repo, gh_comment, .progress = TRUE)
  oarch$gh_commits <- map(oarch$gh_repo, gh_commit, .progress = TRUE)
  saveRDS(oarch, cached_gh_data)
}
oarch <- readRDS(cached_gh_data)

n_repos <- n_filter(oarch, !is.na(gh_repo))
n_commits <- oarch |> drop_na(gh_repo) |> unnest(gh_commits) |> nrow()
n_issues <- oarch |> drop_na(gh_repo) |> unnest(gh_issues) |> nrow()
n_comments <- oarch |> drop_na(gh_repo) |> unnest(gh_comments) |> nrow()
n_contributors <- oarch |> drop_na(gh_repo) |> unnest(gh_contribs) |> 
  distinct(contributor) |> nrow()
```

@@

Where applicable, we obtained more detailed information about each repository's contents and contribution histories from the GitHub API (application programming interface).
We opted to only collect repository data from GitHub because it is the most popular forge platform used by open-archaeo projects (@tbl-forges).
This means that projects that do not use version control (`r percent(p_no_vc)` of the total), or host it elsewhere (`r percent(p_no_github)` of the total), are excluded from these parts of the analysis, though we were still able to perform an analysis of their contents and authorship from the data included in open-archaeo itself.
In total, we analysed data on `r n_repos` repositories, comprising `r n_commits` commits, `r n_issues` issues/pull requests, and `r n_comments` from `r n_contributors` distinct users, as well as repository metadata on programming languages used, licensing, stars and forks, and so on.

Taken together the open-archaeo directory and the supplemental data from the GitHub API provide a rich resource to explore the nature of collaborative software engineering in archaeology.
Here we employ exploratory data analysis [@tukey1977] to identify and characterise overall trends visible in this rich dataset.
In @sec-open-archaeology, our focus is on examining the general state of open source archaeological software and resource development.
In @sec-collaboration, we refine our analysis to examine development processes, with specific focus on collaborative experiences.
Finally, in @sec-network, we apply network analysis methods to investigate the formation of broader collaborative communities.
Our analyses combine to support our objectives of understanding what kinds of software and resources archaeologists are making, and how they create these tools in response to specific needs and use-cases, as afforded by offline social and professional connections, and within the context of an emerging community of practice.

The quantitative analyses and figures presented here were generated with `r version$version.string` [@rcoreteam2023].
The full data and code is available in the compendium that accompanies this paper [@roe2023] <!-- TODO: reference should be updated to reflect the actual version number and date -->.

### 2024-02-02 analysis/_04-open_archaeology.qmd
Update open-archaeo and GitHub data

```{r tbl-categories}
#| tbl-cap: Categories of open archaeology projects
tribble(
  ~category, ~url,                               ~kind,       ~scope,
  "Packages and libraries", "https://open-archaeo.info/categories/packages-and-libraries/",                "Software", "Sets of functions assembled with clear purpose, and made accessible using standards established by an underlying platform.",
  "Standalone software", "https://open-archaeo.info/categories/standalone-software/",                   "Software", "Software that may be operated without needing to first access an underlying platform.",
  "Scripts", "https://open-archaeo.info/categories/scripts/",                               "Software", "Sets of pragmatically assembled mutable functions, often lacking complete documentation or adherence to protocols that would otherwise facilitate secondary use outside their original contexts of creation.",
  "Specifications, protocols and schemas", "https://open-archaeo.info/categories/specifications-protocols-and-schemas/", "Documents", "A formal data structure or framework intended to be used as a model.",
  "Products", "https://open-archaeo.info/categories/products/",                              "Documents", "Stable outcomes of creative work.",
  "Guides", "https://open-archaeo.info/categories/guides/",                                "Documents", "An educational resource or documented protocol meant to instruct readers how to apply relevant tools or techniques.",
  "Lists and datasets", "https://open-archaeo.info/categories/lists-and-datasets/",                    "Documents", "A series of consistently organized observations assembled with purpose."
) |>
  left_join(oarch, by = "category") |>
  count(kind, category, url, scope) |>
  mutate(
    category = glue("[{category}]({url})"),
    p = n / sum(n),
    p = paste0(format(p * 100, trim = TRUE, digits = 1), "%")
  ) |>
  arrange(desc(kind), -n) |>
  select(-kind) |>
  rename_with(tools::toTitleCase) |>
  rename(`%` = p) |>
  tt() |>
  group_tt(list("Software" = 1, "Documents" = 4)) |>
  format_tt(1, markdown = TRUE)
```

@@

```{r tbl-tags}
#| tbl-cap: Themes of open archaeology projects
oarch |>
  pivot_longer(c(tag1, tag2, tag3, tag4, tag5), values_to = "tag",
               values_drop_na = TRUE) |>
  drop_na(tag) |>
  group_by(tag, category) |>
  summarise(n = n(), .groups = "drop_last") |>
  mutate(total = sum(n)) |>
  pivot_wider(names_from = category, values_from = n) |>
  mutate(
    tag = glue("[{tag}](https://open-archaeo.info/{slugify(tag)})"),
    across(everything(), \(x) replace_na(x, 0))
  ) |>
  arrange(-total) |>
  rename(theme = tag) |>
  rename_with(tools::toTitleCase) |>
  tt()
```

@@

```{r fig-github-cumulative}
#| fig-cap: Growth of open archaeology projects on GitHub
p_gh_commits_cum <- oarch |>
  unnest(gh_commits) |>
  drop_na(sha) |>
  mutate(date = floor_date(datetime, "week")) |>
  group_by(category, date) |>
  summarise(n_commits = n(), .groups = "drop_last") |>
  mutate(cum_commits = cumsum(n_commits)) |>
  ggplot(aes(date, cum_commits,
             fill = fct_rev(category),
             colour = fct_rev(category))) +
  geom_area() +
  annotate("segment", 
           x = ymd("2008-04-01", tz = "UTC"), 
           xend = ymd("2008-04-01", tz = "UTC"),
           y = 16000, yend = 4000,
           arrow = arrow(type = "closed", length = unit(0.02, "npc"))) +
  annotate("text", 
           x = ymd("2008-04-01", tz = "UTC"), y = 19000,
           label = "GitHub\nlaunched",
           vjust = 0) +
  scale_x_datetime(limits = c(ymd("2006-12-31", tz = "UTC"), now("UTC")),
                   date_breaks = "2 years", 
                   date_labels = "%Y",
                   expand = c(0,0)) +
  scale_y_continuous(labels = scales::comma) +
  scale_colour_bright(guide = guide_none()) +
  scale_fill_bright() +
  labs(
    y = "Cumulative commits",
    x = NULL, fill = NULL
  ) +
  theme_oarch() +
  theme(legend.position = "top")

p_gh_repos_cum <- oarch |>
  unnest(gh_commits) |>
  drop_na(sha) |>
  group_by(repo) |> 
  filter(datetime == min(datetime)) |> # Only first commits
  mutate(date = floor_date(datetime, "week")) |>
  group_by(category, date) |>
  summarise(n_commits = n(), .groups = "drop_last") |>
  mutate(cat_total = sum(n_commits)) |>
  mutate(cum_commits = cumsum(n_commits)) |>
  select(category, date, cum_commits) |>
  group_by(category) |>
  nest() |>
  mutate(data = map(data, \(x) { # Extend the range of each category to today
    bind_rows(x, list(date = today(), cum_commits = max(x$cum_commits)))
  })) |>
  unnest(c(data)) |>
  ggplot(aes(date, cum_commits,
             fill = fct_rev(category),
             colour = fct_rev(category))) +
  geom_area() +
  annotate("segment",
           x = ymd("2008-04-01", tz = "UTC"),
           xend = ymd("2008-04-01", tz = "UTC"),
           y = 40, yend = 10,
           arrow = arrow(type = "closed", length = unit(0.02, "npc"))) +
  annotate("text",
           x = ymd("2008-04-01", tz = "UTC"), y = 50,
           label = "GitHub\nlaunched",
           vjust = 0) +
  scale_x_datetime(limits = c(ymd("2006-12-31", tz = "UTC"), now("UTC")),
                   date_breaks = "2 years", 
                   date_labels = "%Y",
                   expand = c(0,0)) +
  scale_y_continuous(labels = scales::comma) +
  scale_colour_bright(guide = guide_none()) +
  scale_fill_bright(guide = guide_none()) +
  labs(
    y = "Cumulative repositories",
    x = NULL, fill = NULL
  ) +
  theme_oarch()

@@

As we can see, archaeologists have been using git from even before GitHub was launched in 2008.
But use of git really began to take off around 2014--2015, when we see an uptick in the rate of growth that has continued ever since.

>>>>

```{r tbl-categories}
#| tbl-cap: Categories of open archaeology projects
tribble(
  ~category, ~url,                               ~kind,       ~scope,
  "Packages and libraries", "https://open-archaeo.info/categories/packages-and-libraries/",                "Software", "Sets of functions assembled with clear purpose, and made accessible using standards established by an underlying platform.",
  "Standalone software", "https://open-archaeo.info/categories/standalone-software/",                   "Software", "Software that may be operated without needing to first access an underlying platform.",
  "Scripts", "https://open-archaeo.info/categories/scripts/",                               "Software", "Sets of pragmatically assembled mutable functions, often lacking complete documentation or adherence to protocols that would otherwise facilitate secondary use outside their original contexts of creation.",
  "Specifications, protocols and schemas", "https://open-archaeo.info/categories/specifications-protocols-and-schemas/", "Documents", "A formal data structure or framework intended to be used as a model.",
  "Products", "https://open-archaeo.info/categories/products/",                              "Documents", "Stable outcomes of creative work.",
  "Guides", "https://open-archaeo.info/categories/guides/",                                "Documents", "An educational resource or documented protocol meant to instruct readers how to apply relevant tools or techniques.",
  "Lists and datasets", "https://open-archaeo.info/categories/lists-and-datasets/",                    "Documents", "A series of consistently organized observations assembled with purpose."
) |>
  left_join(oarch, by = "category") |>
  count(kind, category, url, scope) |>
  mutate(
    category = glue("[{category}]({url})"),
    p = n / sum(n),
    p = paste0(format(p * 100, trim = TRUE, digits = 1), "%")
  ) |>
  arrange(desc(kind), -n) |>
  select(category, scope, n, p) |>
  rename_with(tools::toTitleCase) |>
  rename(`%` = p) |>
  tt() |>
  group_tt(list("Software" = 1, "Documents" = 4)) |>
  format_tt(1, markdown = TRUE)
```

@@

```{r tbl-tags}
#| tbl-cap: Themes of open archaeology projects
oarch |>
  pivot_longer(c(tag1, tag2, tag3, tag4, tag5), values_to = "tag",
               values_drop_na = TRUE) |>
  drop_na(tag) |>
  group_by(tag, category) |>
  summarise(n = n(), .groups = "drop_last") |>
  mutate(total = sum(n)) |>
  pivot_wider(names_from = category, values_from = n) |>
  mutate(
    tag = glue("[{tag}](https://open-archaeo.info/tags/{slugify(tag)})"),
    across(everything(), \(x) replace_na(x, 0))
  ) |>
  arrange(-total) |>
  rename(theme = tag) |>
  rename_with(tools::toTitleCase) |>
  tt() |>
  format_tt(1, markdown = TRUE)
```

@@

```{r fig-github-cumulative}
#| fig-cap: Growth of open archaeology projects on GitHub
dt_last_commit <- oarch |> unnest(gh_commits) |> pull(datetime) |> max(na.rm = TRUE)

p_gh_commits_cum <- oarch |>
  unnest(gh_commits) |>
  drop_na(sha) |>
  mutate(date = floor_date(datetime, "week")) |>
  group_by(category, date) |>
  summarise(n_commits = n(), .groups = "drop_last") |>
  mutate(cum_commits = cumsum(n_commits)) |>
  group_by(category) |>
  nest() |>
  mutate(data = map(data, \(x) { # Extend the range of each category to end
    bind_rows(x, list(date = dt_last_commit, cum_commits = max(x$cum_commits)))
  })) |>
  unnest(c(data)) |>
  ggplot(aes(date, cum_commits,
             fill = fct_rev(category),
             colour = fct_rev(category))) +
  geom_area() +
  annotate("segment", 
           x = ymd("2008-04-01", tz = "UTC"), 
           xend = ymd("2008-04-01", tz = "UTC"),
           y = 16000, yend = 4000,
           arrow = arrow(type = "closed", length = unit(0.02, "npc"))) +
  annotate("text", 
           x = ymd("2008-04-01", tz = "UTC"), y = 19000,
           label = "GitHub\nlaunched",
           vjust = 0) +
  scale_x_datetime(limits = c(ymd("2006-12-31", tz = "UTC"), dt_last_commit),
                   date_breaks = "2 years", 
                   date_labels = "%Y",
                   expand = c(0,0)) +
  scale_y_continuous(labels = scales::comma) +
  scale_colour_bright(guide = guide_none()) +
  scale_fill_bright() +
  labs(
    y = "Cumulative commits",
    x = NULL, fill = NULL
  ) +
  theme_oarch() +
  theme(legend.position = "top")

p_gh_repos_cum <- oarch |>
  unnest(gh_commits) |>
  drop_na(sha) |>
  group_by(repo) |> 
  filter(datetime == min(datetime)) |> # Only first commits
  mutate(date = floor_date(datetime, "week")) |>
  group_by(category, date) |>
  summarise(n_repos = n(), .groups = "drop_last") |>
  mutate(cat_total = sum(n_repos)) |>
  mutate(cum_repos = cumsum(n_repos)) |>
  select(category, date, cum_repos) |>
  group_by(category) |>
  nest() |>
  mutate(data = map(data, \(x) { # Extend the range of each category to end
    bind_rows(x, list(date = dt_last_commit, cum_repos = max(x$cum_repos)))
  })) |>
  unnest(c(data)) |>
  ggplot(aes(date, cum_repos,
             fill = fct_rev(category),
             colour = fct_rev(category))) +
  geom_area() +
  annotate("segment",
           x = ymd("2008-04-01", tz = "UTC"),
           xend = ymd("2008-04-01", tz = "UTC"),
           y = 40, yend = 10,
           arrow = arrow(type = "closed", length = unit(0.02, "npc"))) +
  annotate("text",
           x = ymd("2008-04-01", tz = "UTC"), y = 50,
           label = "GitHub\nlaunched",
           vjust = 0) +
  scale_x_datetime(limits = c(ymd("2006-12-31", tz = "UTC"), dt_last_commit),
                   date_breaks = "2 years", 
                   date_labels = "%Y",
                   expand = c(0,0)) +
  scale_y_continuous(labels = scales::comma) +
  scale_colour_bright(guide = guide_none()) +
  scale_fill_bright(guide = guide_none()) +
  labs(
    y = "Cumulative repositories",
    x = NULL, fill = NULL
  ) +
  theme_oarch()

@@

As we can see, archaeologists have been using git from even before GitHub was launched in 2008.
But use of git really began to take off around 2014--2015, when we see an uptick in the rate of growth that has continued ever since.
<!-- TODO: Update and note plateau -->

### 2024-02-02 analysis/_06-network.qmd
Update open-archaeo and GitHub data

# User-user
tbl_graph(nodes = nodes_users(oarch_graph), 
          edges = edges_common_repos(oarch_graph),
          directed = FALSE) |>
  mutate(
    degree = centrality_degree(),
    betweenness = centrality_betweenness(weights = n),
    subgraph = as_factor(group_components()),
    cluster = as_factor(group_edge_betweenness())
  ) ->
  oarch_graph_user_user

@@

```{r fig-graph-repo-user}
#| fig-cap: Graph of open archaeology repositories and users connected by contributions. Darker edges indicate a great number of contributions. Node colour indicates membership of the largest clusters according to the edge–betweenness method [@girvan2002]. Excludes isolate nodes.
g_repo_user <- oarch_graph_repo_user |>
  group_by(cluster) |>
  mutate(cluster_n = n()) |>
  ungroup() |>
  mutate(
    cluster_rank = dense_rank(desc(cluster_n)),
    cluster = if_else(cluster_rank <= 7, cluster, NA)
  ) |>
  ggraph(layout = "fr", niter = 5000, grid = "nogrid") +
  geom_edge_link(aes(group = contrib, alpha = n_contrib)) +
  geom_point_interactive(aes(x, y, colour = cluster, shape=node_type, tooltip = node)) + 
  scale_edge_alpha(trans = "log", guide = guide_none()) +
  scale_colour_discrete(guide = guide_none()) +
  labs(shape = NULL) +
  theme(panel.background = element_rect(fill = "white"), legend.position = "bottom")

@@

<!-- Predictors of repo centrality -->
The repositories most central to the network as a whole [@tbl-repo-betweenness] include several lists and directories, including open-archaeo itself.
Four of the top ten most central repositories (ISAAKiel/mortAAR, ISAAKiel/shapAAR, ISAAKiel/quantAAR, ropensci/c14bazAAR) are associated with the ISAA-Kiel group, emphasising the importance of existing 'real world' collaborations in structuring the network.
Three (ropensci/c14bazAAR, ahb108/rcarbon, Chronomodel/chronomodel) are R packages relating to radiocarbon data and modelling, probably reflecting the fact that this has long been a prominent focus of statistical software development in archaeology.
Repository centrality is predicted by the total number of commits it has received but, somewhat surprisingly, it is younger repositories rather than older ones that tend to be more central.
Tentatively, we interpret this as an indication that the network has become more connected over time, but we leave a fuller analysis of temporal trends in collaborative activity to future work.

>>>>

# User-user
tbl_graph(nodes = nodes_users(oarch_graph), 
          edges = edges_common_repos(oarch_graph),
          directed = FALSE) |>
  mutate(
    degree = centrality_degree(),
    betweenness = centrality_betweenness(weights = n),
    subgraph = as_factor(group_components()),
    cluster = as_factor(group_edge_betweenness()) # <- slow!
  ) ->
  oarch_graph_user_user

@@

```{r fig-graph-repo-user}
#| fig-cap: Graph of open archaeology repositories and users connected by contributions. Darker edges indicate a great number of contributions. Node colour indicates membership of the largest clusters according to the edge–betweenness method [@girvan2002]. Excludes isolate nodes.
g_repo_user <- oarch_graph_repo_user |>
  group_by(cluster) |>
  mutate(cluster_n = n()) |>
  ungroup() |>
  mutate(
    cluster_rank = dense_rank(desc(cluster_n)),
    cluster = if_else(cluster_rank <= 7, cluster, NA)
  ) |>
  ggraph(layout = "fr", niter = 5000, grid = "nogrid") +
  geom_edge_link(aes(group = contrib, alpha = n_contrib)) +
  geom_point_interactive(aes(x, y, colour = cluster, shape = node_type, 
                             tooltip = node)) + 
  scale_edge_alpha(trans = "log", guide = guide_none()) +
  scale_colour_discrete(guide = guide_none()) +
  labs(shape = NULL) +
  theme(panel.background = element_rect(fill = "white"), 
        legend.position = "bottom")

@@

<!-- Predictors of repo centrality -->
<!-- TODO: Needs an update. These repos are no longer in the top 10, and it's probably best not to be so specific given how volatile that is. -->
The repositories most central to the network as a whole [@tbl-repo-betweenness] include several lists and directories, including open-archaeo itself.
Four of the top ten most central repositories (ISAAKiel/mortAAR, ISAAKiel/shapAAR, ISAAKiel/quantAAR, ropensci/c14bazAAR) are associated with the ISAA-Kiel group, emphasising the importance of existing 'real world' collaborations in structuring the network.
Three (ropensci/c14bazAAR, ahb108/rcarbon, Chronomodel/chronomodel) are R packages relating to radiocarbon data and modelling, probably reflecting the fact that this has long been a prominent focus of statistical software development in archaeology.
Repository centrality is predicted by the total number of commits it has received but, somewhat surprisingly, it is younger repositories rather than older ones that tend to be more central.
Tentatively, we interpret this as an indication that the network has become more connected over time, but we leave a fuller analysis of temporal trends in collaborative activity to future work.

### 2024-02-02 analysis/openarchaeo_collaboration.qmd
Update open-archaeo and GitHub data

library("english")
library("fs")
library("ggiraph")
library("ggraph")
library("here")
library("khroma")
library("lubridate")
library("patchwork")
library("rgexf")
library("scales")
library("tidygraph")
library("tidyverse")
library("tinytable")
```

>>>>

library("english")
library("fs")
library("ggiraph")
library("ggraph")
library("glue")
library("here")
library("khroma")
library("lubridate")
library("patchwork")
library("rgexf")
library("scales")
library("tidygraph")
library("tidyverse")
library("tinytable")
```
